An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-07-09 EconGrowth.Rnw
Turned off tikz.
Now using ternary plots for resample data for CD and CDe models in the paper.

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
# Provides access to data melting. 
# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
require(reshape2) 
# tikz allows use of LaTeX formatting and font in graphs. 
# Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
# on installing tikzDevice.
# require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
opts_chunk$set(
  # ********************************************************
  eval=FALSE,
  # ********************************************************
  # tikz allows LaTeX code in graphical output. 
  # E.g., "$y$" for a variable name in the legend for a graph.  
  # dev='tikz',    
  tidy=FALSE,
  comment=NA,
  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  # Turns off messages for all chunks. 
  # Set TRUE on an individual chunk to see it.
  message=FALSE, 
  # Tells whether to echo code for all chunks. 
  # Set TRUE on an individual chunk to see its code.
  echo=FALSE     
)
source("Econ-Growth-Functions2.R")
source("Graphics.R")
@

@@

@@

<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.", eval=TRUE>>=
cdeResampleTrianglePlot(energyType="Q")
@

@@

<<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.", eval=TRUE>>=
cdeResampleTrianglePlot(energyType="X")
@

**** Add triangle cloud plots for $x$ and $u$ if we decide to use these plots. ****

>>>>

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
# Provides access to data melting. 
# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
require(reshape2) 
# tikz allows use of LaTeX formatting and font in graphs. 
# Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
# on installing tikzDevice.
# require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
opts_chunk$set(
  # ********************************************************
  eval=TRUE,
  # ********************************************************
  # tikz allows LaTeX code in graphical output. 
  # E.g., "$y$" for a variable name in the legend for a graph.  
  # dev='tikz',
  tidy=FALSE,
  comment=NA,
  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  # Turns off messages for all chunks. 
  # Set TRUE on an individual chunk to see it.
  message=FALSE, 
  # Tells whether to echo code for all chunks. 
  # Set TRUE on an individual chunk to see its code.
  echo=FALSE     
)
source("Econ-Growth-Functions2.R")
source("Graphics.R")
@

@@

Figure~\ref{fig:CD_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (without energy). $\gamma$ is always 0.0, because energy is not included in this model.

<<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType=NA)
@

@@

<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
cdResampleTrianglePlot(energyType="Q")
@

@@

<<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.">>=
cdResampleTrianglePlot(energyType="X")
@

Figure~\ref{fig:CDu_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $u$).

<<CDu_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Cobb-Douglas (with $u$) resample model parameters.">>=
cdResampleTrianglePlot(energyType="U")
@
